---
title: "Univariate - MA Data Analysis"
author: "Akihiko Mori"
output: 
  rmdformats::readthedown:
  # pdf_document:
  # html_document:
    # toc: true
    # theme: united
    # code_folding: hide
---


```{r setup, include = FALSE}
## setup for r codes included
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(fig.show="hold", out.width="50%") 
```

```{r packages, echo=FALSE,message = FALSE, warning=FALSE}
## Library ---
library(bayesforecast)
library(dplyr)
library(forecast)
library(ggplot2) # ggplot
library(ggpubr)
library(gridExtra) # grid.arrange function
library(lubridate) # wday function
library(rstatix)
library(stargazer)
library(tidyverse)
library(fpp3, seasonal)

library(tables)
library(modelsummary)
```


```{r data import, echo=FALSE,message = FALSE, warning=FALSE}
## Import Data from file ---
rm(df)
dataPass = "/Users/am/Library/CloudStorage/OneDrive-UNBC/00MAthesis/ma24r/ma24data"
df <- read_csv(dataPass)
df$day <- factor(df$day, levels = c("Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))
rm(dataPass)
```

<!-- ### Check imported data -->
<!-- ```{r check data} -->
<!-- head(df) -->
<!-- str(df) -->
<!-- names(df) -->
<!-- ``` -->

# Univariable ---
## Open days
```{r open days}
# sample size: open and close days ---------------------------------------
data.frame(obs_days    = nrow(df),
           open_days   = sum(df$is_closed),
           closed_days = sum(!df$is_closed))
df %>% 
  freq_table(is_closed)

df <- as.data.frame(df)

datasummary(is_closed + 1 ~ N + Percent(), 
            data = df, type = "logical")

datasummary(food_waste_kg + solid_waste_kg + liquid_waste_kg ~ Mean  + Min + Median + Max + SD
  ,data = df, output = "latex")

library(parameters)
skewness(df$food_waste_kg,type = 1)
skewness(df$solid_waste_kg,type = 1)
skewness(df$liquid_waste_kg,type = 1)
# Skewness
# Symmetric distributions have a skewness around zero, while a negative skewness values indicates a "left-skewed" distribution, and a positive skewness values indicates a "right-skewed" distribution. Examples for the relationship of skewness and distributions are:
# 
# Normal distribution (and other symmetric distribution) has a skewness of 0
# 
# Half-normal distribution has a skewness just below 1
# 
# Exponential distribution has a skewness of 2
# 
# Lognormal distribution can have a skewness of any positive value, depending on its parameters
# 
# (https://en.wikipedia.org/wiki/Skewness)
# Types of Skewness
# skewness() supports three different methods for estimating skewness, as discussed in Joanes and Gill (1988):
# 
# Type "1" is the "classical" method, which is g1 = (sum((x - mean(x))^3) / n) / (sum((x - mean(x))^2) / n)^1.5
# 
# Type "2" first calculates the type-1 skewness, than adjusts the result: G1 = g1 * sqrt(n * (n - 1)) / (n - 2). This is what SAS and SPSS usually return
# 
# Type "3" first calculates the type-1 skewness, than adjusts the result: b1 = g1 * ((1 - 1 / n))^1.5. This is what Minitab usually returns.

# df %>% 
#   select(c(date, day, is_closed))%>%
#   subset(is_closed == TRUE)
  
```


## Basic Summary of Dependent Variables
```{r basic summary}
# basic summary: dependents ----------------------------------------------------
# data.frame(food_loss_waste   = c(summary(df$food_loss_kg + df$food_waste_kg)),
#            food_loss         = c(summary(df$food_loss_kg)),
#            food_waste_all    = c(summary(df$food_waste_kg)),
#            food_waste_liquid = c(summary(df$liquid_waste_kg)),
#            food_waste_solid  = c(summary(df$solid_waste_kg)))
# df %>% 
#   select(c(food_loss_kg,food_waste_kg,liquid_waste_kg,solid_waste_kg)) %>% 
#   get_summary_stats()

# library(summarytools)
# df %>%
#   select(c(food_loss_kg,food_waste_kg,
#            liquid_waste_kg,solid_waste_kg)) %>% 
#   descr(order = "preserve",
#         stats = c('mean', 'sd', 'min', 'q1', 'med', 'q3', 'max'),
#         round.digits = 6)

# basic summary: dependents excluding closed days ------------------------------
# data.frame(food_loss_waste   = c(summary(df$food_loss_kg[!df$is_closed] 
#                                          + df$food_waste_kg[!df$is_closed])),
#            food_loss         = c(summary(df$food_loss_kg[!df$is_closed])),
#            food_waste_all    = c(summary(df$food_waste_kg[!df$is_closed])),
#            food_waste_liquid = c(summary(df$liquid_waste_kg[!df$is_closed])),
#            food_waste_solid  = c(summary(df$solid_waste_kg[!df$is_closed])))
df %>% 
  filter(is_closed == FALSE) %>%
  rstatix::select(c(food_loss_kg,food_waste_kg,liquid_waste_kg,solid_waste_kg)) %>% 
  get_summary_stats()
# library(stargazer)
# df_fw <- as.data.frame(subset(df, is_closed==FALSE, 
#                  select = c("food_loss_kg","food_waste_kg",
#                             "liquid_waste_kg","solid_waste_kg")))
# stargazer(df_fw, type = "latex")
```


```{r stargazer dependents}
# summary of--------------------
# 1. number of observations
# 2. Averages
# 3. standard deviations
# 4. Min values
# 4. Max values
# stargazer(subset(df[4:7], df$is_closed == FALSE),  flip=TRUE,
#           type = "text",digits=2, out="deps1.txt")
# 
# # Excluding the restaurant closed ---------------
# stargazer(subset(df[4:7], df$is_closed == FALSE),  flip=TRUE,
#           type = "text",digits=2, out="deps2.txt")
```


# Histograms ---
<!-- ## X Normal histogram -->
<!-- ```{r normal histogram} -->
<!-- # Create a data frame of numeric features & label -->
<!-- dep_features <- df %>%  -->
<!--   rstatix::select(c(is_closed, food_loss_kg, food_waste_kg,  -->
<!--            solid_waste_kg, liquid_waste_kg)) -->

<!-- # Pivot data to a long format -->
<!-- dep_features <- dep_features %>%  -->
<!--   pivot_longer(!is_closed, names_to = "features",  -->
<!--                values_to = "values") %>% -->
<!--   group_by(features) %>%  -->
<!--   mutate(Mean = mean(values), -->
<!--          Median = median(values)) -->


<!-- # Plot a histogram for each feature -->
<!-- dep_features %>% -->
<!--   ggplot() + -->
<!--   geom_histogram(aes(x = values, fill = features),  -->
<!--                  bins = 100, alpha = 0.7, show.legend = F) + -->
<!--   facet_wrap(~ features, scales = 'free')+ -->
<!--   paletteer::scale_fill_paletteer_d("ggthemes::excel_Parallax") + -->
<!--   # Add lines for mean and median -->
<!--   geom_vline(aes(xintercept = Mean, color = "Mean"),  -->
<!--              linetype = "dashed", linewidth = 1 ) + -->
<!--   geom_vline(aes(xintercept = Median, color = "Median"),  -->
<!--              linetype = "dashed", linewidth = 1 ) + -->
<!--   scale_color_manual(name = "",  -->
<!--                      values = c(Mean = "red", Median = "yellow"))  -->
<!-- ``` -->

## X Histogram with density
```{r histograms}
# binwidth = bw
# bw <- 2 * IQR(df$food_loss_kg) / length(df$food_loss_kg)^(1/3)
# Histogram on food loss + food waste ------------------------------------------
hist_loss_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = food_loss_kg + food_waste_kg)) +
  geom_histogram(aes(y = after_stat(density)), bins = 30, colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Food Loss and Food Waste - Histogram")
hist_loss_waste

# Histogram on food loss----------------------------------------------------
hist_loss <- 
  ggplot(data = subset(df, is_closed %in% FALSE), aes(x = food_loss_kg)) +
  geom_histogram(aes(y = after_stat(density)), bins = 30, colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Food Loss - Histogram")
hist_loss

# Histogram of food waste ----------------------------------------------------
hist_food_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = food_waste_kg)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30, colour = "black", fill = "white") +
  geom_density(linewidth = 1.5, colour = "black", 
               fill = 4, alpha = 0.15) +
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "Food Waste - Histogram")
hist_food_waste

# Histogram of solid waste ----------------------------------------------------
hist_solid_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), aes(x = solid_waste_kg)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = "orange", fill = "white") +
  geom_density(linewidth = 1.5, colour = "orange", 
               fill = 4, alpha = 0.15) +
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "Solid Food Waste - Histogram")
hist_solid_waste

# Histogram of liquid waste ----------------------------------------------------
hist_liquid_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), aes(x = liquid_waste_kg)) +
  geom_histogram(aes(y = after_stat(density)),
                 bins = 30,colour = "dark blue", fill = "white") +
  geom_density(linewidth = 1.5, colour = "dark blue", 
               fill = 4, alpha = 0.15) +
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "Liquid Food Waste - Histogram")
hist_liquid_waste

hist_fws <- ggarrange(hist_food_waste,
                     hist_solid_waste,
                     hist_liquid_waste,
                     ncol=2, nrow=2)
hist_fws
ggsave("hist_fws.pdf",hist_fws)
unlink("food_waste_tsplot.pdf")
```
#### Q-Q plot
```{r QQ plot dep vars.}
# Food loss ------------

# Food waste ------------
qq_fw <- ggqqplot(subset(df$food_waste_kg, 
                         df$is_closed %in% FALSE)) +
  xlab("theoretical") + ylab("sample") +
  ggtitle("Food Waste in kg")

# Solid Food waste ------------
qq_sfw <- ggqqplot(subset(df$solid_waste_kg, 
                          df$is_closed %in% FALSE),
         color = "dark orange") +
  xlab("theoretical") + ylab("sample") +
  ggtitle("Solid Food Waste in kg")

# Liquid Food waste ------------
qq_lfw <- ggqqplot(subset(df$liquid_waste_kg, 
                          df$is_closed %in% FALSE),
         color = "dark blue") +
  xlab("theoretical") + ylab("sample") +
  ggtitle("Liquid Food Waste in kg")

qq_fws <- ggarrange(qq_fw,qq_sfw,qq_lfw,
                    ncol=2, nrow=2)
qq_fws
ggsave("qq_fws.pdf",qq_fws)
unlink("food_waste_tsplot.pdf")
```

## X shapiro test
```{r}
# Food waste ------------
df %>% 
  filter(is_closed == FALSE) %>%
  shapiro_test(food_waste_kg, solid_waste_kg, liquid_waste_kg)
```
From the output, all the p-value is far less than 0.05; so implying that the distribution of the data are significantly different from normal distribution. In other words, we can not assume the normality.

## Histogram Food Waste per customer
```{r histograms_customer}
# Histogram of food waste -------------------------------------------
hist_food_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = food_waste_kg/customers)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Food Waste per Customer - Histogram")
hist_food_waste

# Histogram of solid waste --------------------------------------------
hist_solid_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE),
         aes(x = solid_waste_kg/customers)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Solid Food Waste per Customer - Histogram")
hist_solid_waste

# Histogram of liquid waste ----------------------------------------
hist_liquid_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = liquid_waste_kg/customers)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Liquid Food Waste per Customer - Histogram")
hist_liquid_waste

# grid.arrange(hist_loss_waste,hist_loss,
#              hist_food_waste,hist_solid_waste,hist_liquid_waste)
```


\newpage
## Q-Q plot Food Waste per customer
```{r QQ plot dep vars.per customer}
# Food waste ------------
ggqqplot(subset(df$food_waste_kg/df$customers, 
                df$is_closed %in% FALSE)) +
  xlab("theoretical") + ylab("sample") +
  ggtitle("QQ plot of Food Waste per Customer in kg")

# Solid Food waste ------------
ggqqplot(subset(df$solid_waste_kg/df$customers, 
                df$is_closed %in% FALSE),
         color = "dark orange") +
  xlab("theoretical") + ylab("sample") +
  ggtitle("QQ plot of Solid Food Waste per Customer in kg")

# Liquid Food waste ------------
ggqqplot(subset(df$liquid_waste_kg/df$customers, 
                df$is_closed %in% FALSE),
         color = "dark blue") +
  xlab("theoretical") + ylab("sample") +
  ggtitle("QQ plot of Liquid Food Waste per Customer in kg")
```

## shapiro test for per customer
```{r}
# Food waste ------------
df %>% 
  filter(is_closed == FALSE) %>%
  mutate(food_waste_p_kg   = food_waste_kg/customers,
         solid_waste_p_kg  = solid_waste_kg/customers,
         liquid_waste_p_kg = liquid_waste_kg/customers) %>%
  shapiro_test(food_waste_p_kg, solid_waste_p_kg, liquid_waste_p_kg) 
```

From the output, the p-value of solid food waste per customer is far less that the significant level of 0.05; but the others are not. So it imply that the distribution of the data for solid food waste per customer is significantly different from normal distribution. 
In other words, we can assume the normality for food waste and liquid food waste per customer but not for solid food waste.


<!-- ## X Histogram per customer w/o outlier -->
<!-- ```{r histograms_customer w/o outlier} -->
<!-- # find outliers ---- -->
<!-- # food waste ----- -->
<!-- which(df$food_waste_kg/df$customers > 0.2)  # => 46 -->
<!-- which(df$solid_waste_kg/df$customers > 0.1) # => 46 -->
<!-- df[46,]$date -->
<!-- # outlier is 46; 2022-11-08 -->

<!-- # Histogram of food waste ------------------------------------------- -->
<!-- hist_food_waste <-  -->
<!--   df %>%  -->
<!--   filter(is_closed %in% FALSE) %>% -->
<!--   filter(!row_number() %in% c(45)) %>% -->
<!--   ggplot(aes(x = food_waste_kg/customers)) + -->
<!--   geom_histogram(aes(y = after_stat(density)),  -->
<!--                  bins = 30,colour = 1, fill = "white") + -->
<!--   geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) + -->
<!--   labs(title = "Food Waste - Histogram") -->
<!-- hist_food_waste -->

<!-- # Histogram of solid waste -------------------------------------------- -->
<!-- hist_solid_waste <-  -->
<!--   df %>%  -->
<!--   filter(is_closed %in% FALSE) %>% -->
<!--   filter(!row_number() %in% c(45)) %>% -->
<!--   ggplot(aes(x = solid_waste_kg/customers)) + -->
<!--   geom_histogram(aes(y = after_stat(density)),  -->
<!--                  bins = 30,colour = 1, fill = "white") + -->
<!--   geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) + -->
<!--   labs(title = "Solid Food Waste - Histogram") -->
<!-- hist_solid_waste -->

<!-- # Histogram of liquid waste ---------------------------------------- -->
<!-- hist_liquid_waste <-  -->
<!--   df %>%  -->
<!--   filter(is_closed %in% FALSE) %>% -->
<!--   filter(!row_number() %in% c(45)) %>% -->
<!--   ggplot(aes(x = liquid_waste_kg/customers)) + -->
<!--   geom_histogram(aes(y = after_stat(density)),  -->
<!--                  bins = 30,colour = 1, fill = "white") + -->
<!--   geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) + -->
<!--   labs(title = "Liquid Food Waste - Histogram") -->
<!-- hist_liquid_waste -->

<!-- grid.arrange(hist_food_waste,hist_solid_waste, -->
<!--              hist_liquid_waste) -->
<!-- ``` -->



<!-- ## Q-Q plot per capita w/o outlier -->
<!-- ```{r QQ plot dep vars.per customer w/o outlier} -->
<!-- library(qqplotr) -->
<!-- # Food waste ------------ -->
<!-- # df %>%  -->
<!-- #   filter(is_closed == FALSE) %>% -->
<!-- #   filter(!row_number() %in% c(45)) %>% -->
<!-- #   ggplot(aes(sample = liquid_waste_kg/customers)) + -->
<!-- #   stat_qq() + stat_qq_line() + -->
<!-- ggqqplot(subset(df[-46,]$food_waste_kg/df[-46,]$customers,  -->
<!--                 df[-46,]$is_closed %in% FALSE)) + -->
<!--   xlab("theoretical") + ylab("sample") + -->
<!--   ggtitle("QQ plot of Food Waste per Customer in kg") -->

<!-- # Solid Food waste ------------ -->
<!-- ggqqplot(subset(df[-46,]$solid_waste_kg/df[-46,]$customers,  -->
<!--                 df[-46,]$is_closed %in% FALSE)) + -->
<!--   xlab("theoretical") + ylab("sample") + -->
<!--   ggtitle("QQ plot of Solid Food Waste per Customer in kg") -->

<!-- # Liquid Food waste ------------ -->
<!-- ggqqplot(subset(df[-46,]$liquid_waste_kg/df[-46,]$customers,  -->
<!--                 df[-46,]$is_closed %in% FALSE)) + -->
<!--   xlab("theoretical") + ylab("sample") + -->
<!--   ggtitle("QQ plot of Liquid Food Waste per Customer in kg") -->
<!-- ``` -->

<!-- ## shapiro test for per capita w/o outlier -->
<!-- ```{r} -->
<!-- # Food waste ------------ -->
<!-- df %>%  -->
<!--   filter(is_closed %in% FALSE) %>% -->
<!--   filter(!row_number() == 45) %>% -->
<!--   mutate(food_waste_p_kg   = food_waste_kg/customers, -->
<!--          solid_waste_p_kg  = solid_waste_kg/customers, -->
<!--          liquid_waste_p_kg = liquid_waste_kg/customers) %>% -->
<!--   shapiro_test(food_waste_p_kg, solid_waste_p_kg, liquid_waste_p_kg) -->
<!-- ``` -->

<!-- From the output, the p-value of solid food waste per customer is far less that the significant level of 0.05; but the others are not. So it imply that the distribution of the data for solid food waste per customer is significantly different from normal distribution.  -->
<!-- In other words, we can assume the normality for food waste and liquid food waste per customer but not for solid food waste. -->

<!-- ## Histogram weekdays_ends -->
<!-- ```{r histograms_customer_weekend} -->
<!-- # Histogram of food waste ------------------------------------------- -->
<!-- hist_food_waste_wk <-  -->
<!--   ggplot(data = subset(df, is_closed %in% FALSE),  -->
<!--          aes(x = food_waste_kg/customers,  -->
<!--              colour = factor(week_end))) + -->
<!--   geom_histogram(aes(y = after_stat(density) ),  -->
<!--                  fill = "white", bins = 30) + -->
<!--   geom_density(linewidth = 1, fill = 4, alpha = 0.15) + -->
<!--   labs(title = "Food Waste - Histogram") -->
<!-- hist_food_waste_wk -->

<!-- # Histogram of solid waste -------------------------------------------- -->
<!-- hist_solid_waste_wk <-  -->
<!--   ggplot(data = subset(df, is_closed %in% FALSE), -->
<!--          aes(x = solid_waste_kg/customers, -->
<!--              colour = factor(week_end))) + -->
<!--   geom_histogram(aes(y = after_stat(density)),  -->
<!--                  bins = 30, fill = "white") + -->
<!--   geom_density(linewidth = 1, fill = 4, alpha = 0.15) + -->
<!--   labs(title = "Solid Food Waste - Histogram") -->
<!-- hist_solid_waste_wk -->

<!-- # Histogram of liquid waste ---------------------------------------- -->
<!-- hist_liquid_waste_wk <-  -->
<!--   ggplot(data = subset(df, is_closed %in% FALSE),  -->
<!--          aes(x = liquid_waste_kg/customers,  -->
<!--              colour = factor(week_end))) + -->
<!--   geom_histogram(aes(y = after_stat(density)),  -->
<!--                  bins = 30, fill = "white") + -->
<!--   geom_density(linewidth = 1, fill = 4, alpha = 0.15) + -->
<!--   labs(title = "Liquid Food Waste - Histogram") -->
<!-- hist_liquid_waste_wk -->

<!-- grid.arrange(hist_food_waste_wk, -->
<!--              hist_solid_waste_wk, -->
<!--              hist_liquid_waste_wk) -->
<!-- ``` -->

## Histogram log Food Waste
```{r histograms_log}
# Histogram of food waste -------------------------------------------
hist_log_food_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = log(food_waste_kg+1))) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Log Food Waste - Histogram")
hist_log_food_waste

# Histogram of solid waste --------------------------------------------
hist_log_solid_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE),
         aes(x = log(solid_waste_kg+1))) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = "orange", fill = "white") +
  geom_density(linewidth = 1.5, colour = "orange", fill = 4, alpha = 0.15) +
  labs(title = "Log Solid Food Waste - Histogram")
hist_log_solid_waste

# Histogram of liquid waste ----------------------------------------
hist_log_liquid_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = log(liquid_waste_kg+1))) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = "dark blue", fill = "white") +
  geom_density(linewidth = 1.5, colour = "dark blue", fill = 4, alpha = 0.15) +
  labs(title = "Log Liquid Food Waste - Histogram")
hist_log_liquid_waste

hist_log_fws <- ggarrange(hist_log_food_waste,
                          hist_log_solid_waste,
                          hist_log_liquid_waste,
                          ncol=2, nrow=2)
hist_log_fws
ggsave("hist_log_fws.pdf",hist_log_fws)
unlink("hist_log_fws.pdf")
```


\newpage
## Q-Q plot log Food Waste
```{r QQ plot logged dep vars }
# Food waste ------------
qq_log_fw <- ggqqplot(subset(log(df$food_waste_kg+1), 
                df$is_closed %in% FALSE)) +
  xlab("theoretical") + ylab("sample") +
  ggtitle("QQ plot of log Food Waste in kg")

# Solid Food waste ------------
qq_log_sfw <- ggqqplot(subset(log(df$solid_waste_kg+1), 
                df$is_closed %in% FALSE),
         color = "dark orange") +
  xlab("theoretical") + ylab("sample") +
  ggtitle("QQ plot of Log Solid Food Waste in kg")

# Liquid Food waste ------------
qq_log_lfw <- ggqqplot(subset(log(df$liquid_waste_kg+1), 
                df$is_closed %in% FALSE),
         color = "dark blue") +
  xlab("theoretical") + ylab("sample") +
  ggtitle("QQ plot of Log Liquid Food Waste in kg")

qq_log_fws <- ggarrange(qq_log_fw,qq_log_sfw,qq_log_lfw,
                    ncol=2, nrow=2)
qq_log_fws
ggsave("qq_log_fws.pdf",qq_log_fws)
unlink("qq_log_fws.pdf")
```

## shapiro test for log food waste
```{r}
# Food waste ------------
df %>% 
  filter(is_closed == FALSE) %>%
  mutate(log_food_waste_kg   = log(food_waste_kg+1),
         log_solid_waste_kg  = log(solid_waste_kg+1),
         log_liquid_waste_kg = log(liquid_waste_kg+1)) %>%
  shapiro_test(log_food_waste_kg, log_solid_waste_kg, log_liquid_waste_kg)
```

# Time Series Plots ---
## Daily Time Series
```{r add month_day_name, echo=FALSE}
# add month_name (September, ..., March) to data frame -------------------------
df <- df %>% 
  mutate(month_name = format(as.Date(df$date), format = "%b")) %>%
  mutate(month_name = factor(month_name, levels = c('Sep','Oct','Nov','Dec',
                                                    'Jan','Feb','Mar')))
# add day_name (1, ..., 30,31) to data frame -----------------------------------
df <- df %>% 
  mutate(day_name = format(as.Date(df$date), format = "%d"))
```


```{r plot daily}
# df[,"is_closed"] <- ifelse(df$is_closed %in% FALSE, "opne", "close")

# Daily Plot on food loss + food waste ---------------------------------
# daily_loss_waste <- 
#   ggplot(data = df, aes(x = as.Date(date), 
#                         y = food_loss_kg + food_waste_kg)) +
#   geom_line(aes(group = 1), color="dark blue") +
#   geom_point(aes(shape = is_closed)) +
#   scale_shape_manual(values=c(16, 4)) +
#   scale_x_date(date_labels = "%b %d") +
#   theme(legend.position = c(0.05,0.15)) +
#   xlab("Date") + ylab("Daily Food Loss and Waste (kg)") +
#   ggtitle("Daily Food Loss and Waste Trend")
# daily_loss_waste

# Daily Plot on food loss ------------------------------------------------
# daily_loss <- 
#   ggplot(data = df, aes(x = as.Date(date), y = food_loss_kg)) +
#   geom_line(color="blue") +
#   geom_point(aes(shape = is_closed)) +
#   scale_x_date(date_labels = "%b %d") +
#   scale_shape_manual(values=c(16, 4))+
#   theme(legend.position = c(0.9,0.85)) +
#   xlab("Date") + ylab("Daily Food Loss (kg)") +
#   ggtitle("Daily Food Loss Trend")
# daily_loss
library(ggpubr)

# Daily Plot on food waste -----------------------------------------------
daily_waste <- 
  ggplot(data = df, aes(x = as.Date(date), y = food_waste_kg)) +
  geom_line(color="black") +
  geom_point(aes(shape = is_closed)) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE,
              linetype = "dashed",color="black") +
  scale_x_date(date_labels = "%b %d") +
  scale_shape_manual(values=c(4,16))+
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none") +
  xlab("Date") + ylab("Daily Food Waste (kg)")
  # ggtitle("Daily Food Waste Trend")
daily_waste
# ggsave("daily_waste.pdf")
# unlink("daily_waste.pdf")

# Daily Plot on solid food waste -----------------------------------------
daily_solid_waste <- 
  ggplot(data = df, aes(x = as.Date(date), y = solid_waste_kg)) +
  geom_line(color="dark orange") +
  geom_point(aes(shape = is_closed)) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE,
              linetype = "dashed",color="black") +
  scale_x_date(date_labels = "%b %d") +
  scale_shape_manual(values=c(4,16))+
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none") +
  xlab("Date") + ylab("Daily Solid Food Waste (kg)") 
  # ggtitle("Daily Solid Food Waste Trend")
daily_solid_waste
# ggsave("daily_solid_waste.pdf")
# unlink("daily_solid_waste.pdf")

# Daily Plot on liquid food waste ----------------------------------------
daily_liquid_waste <- 
  ggplot(data = df, aes(x = as.Date(date), y = liquid_waste_kg)) +
  geom_line(color="dark blue") +
  # geom_line(color="blue", linetype = "dashed") +
  geom_point(aes(shape = is_closed)) +
   geom_smooth(method = "lm", formula = y ~ x, se = FALSE,
               linetype = "dashed",color="black") +
  scale_x_date(date_labels = "%b %d") +
  scale_shape_manual(values=c(4,16))+
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none") +
  xlab("Date") + ylab("Daily Liquid ood Waste (kg)")
  # ggtitle("Daily Liquid Food Waste Trend")
daily_liquid_waste
# ggsave("daily_liquid_waste.pdf")
# unlink("daily_liquid_waste.pdf")

food_waste_tsplot <-
  ggarrange(daily_waste,
               daily_solid_waste,
               daily_liquid_waste, 
            ncol=1, nrow=3, common.legend = TRUE, legend="bottom")
food_waste_tsplot
ggsave("food_waste_tsplot.pdf",food_waste_tsplot)
unlink("food_waste_tsplot.pdf")

df[,"is_closed"] <- ifelse(df$is_closed %in% "open", FALSE, TRUE)
```

## Daily plot per customer
```{r plot daily_p}
# Daily Plot on food waste -----------------------------------------------
daily_waste_p <- 
  ggplot(data = subset(df, is_closed == FALSE),
         aes(x = as.Date(date), y = food_waste_kg/customers)) +
  geom_line(color="black") +
  geom_point(aes(shape = is_closed)) +
  geom_smooth(method = "loess", formula = y ~ x) +
  scale_x_date(date_labels = "%b %d") +
  scale_shape_manual(values=c(16, 4))+
  theme(legend.position = c(0.8,0.85)) +
  xlab("Date") + ylab("Daily Food Waste per Customer (kg)") +
  ggtitle("Daily Food Waste per Customer Trend")
daily_waste_p

# Daily Plot on solid food waste -----------------------------------------
daily_solid_waste_p <- 
  ggplot(data = subset(df, is_closed == FALSE),
         aes(x = as.Date(date), y = solid_waste_kg/customers)) +
  geom_line(color="dark orange") +
  geom_point(aes(shape = is_closed)) +
  geom_smooth(method = "loess", formula = y ~ x) +
  scale_x_date(date_labels = "%b %d") +
  scale_shape_manual(values=c(16, 4))+
  theme(legend.position = c(0.8,0.85)) +
  xlab("Date") + ylab("Daily Solid Food Waste per Customer (kg)") +
  ggtitle("Daily Solid Food Waste per Customer Trend")
daily_solid_waste_p

# Daily Plot on liquid food waste ----------------------------------------
daily_liquid_waste_p <- 
  ggplot(data = subset(df, is_closed == FALSE),
         aes(x = as.Date(date), y = liquid_waste_kg/customers)) +
  geom_line(color="dark blue") +
  geom_line(color="blue", linetype = "dashed") +
  geom_point(aes(shape = is_closed)) +
   geom_smooth(method = "loess", formula = y ~ x) +
  scale_x_date(date_labels = "%b %d") +
  scale_shape_manual(values=c(16, 4))+
  theme(legend.position = c(0.8,0.85)) +
  xlab("Date") + ylab("Daily Liquid ood Waste per Customer (kg)") +
  ggtitle("Daily Liquid Food Waste per Customer Trend")
daily_liquid_waste_p
```


\newpage
## Decompsiotion
```{r decomposition}
df %>%
  as_tsibble(index = date) %>%
  rstatix::select(food_waste_kg) %>%
  fill_gaps(food_waste_kg = 0) %>%
  model(STL(food_waste_kg)) |>
  components() |>
  autoplot()

auto.arima(df$food_waste_kg, trace = TRUE)
auto.arima(df$solid_waste_kg, trace = TRUE)
auto.arima(df$liquid_waste_kg, trace = TRUE)
# 
# auto.arima(df[1:92,]$food_waste_kg, trace = TRUE)
# auto.arima(df[1:92,]$solid_waste_kg, trace = TRUE)
# auto.arima(df[1:92,]$liquid_waste_kg, trace = TRUE)
# 
# auto.arima(df[93:169,]$food_waste_kg, trace = TRUE)
# auto.arima(df[93:169,]$solid_waste_kg, trace = TRUE)
# auto.arima(df[93:169,]$liquid_waste_kg, trace = TRUE)
```


<!-- \newpage -->
<!-- ```{r plot monthly} -->
<!-- # Monthly Plot on food loss and food waste --------------------------------- -->
<!-- monthly_loss_waste <-  -->
<!--   ggplot(data = df, aes(x = day_name,  -->
<!--                         y = food_loss_kg + food_waste_kg, group=1)) + -->
<!--   geom_line(color="dark blue") + -->
<!--   geom_point(aes(shape = is_closed)) + -->
<!--   scale_shape_manual(values=c(16, 4)) + -->
<!--   theme(legend.position = "none") + -->
<!--   # geom_rect(data = df, aes(xmin = date, xmax = dplyr::lead(date), -->
<!--   #                          ymin = -Inf, ymax = Inf, -->
<!--   #                          fill = factor(!is_closed)),  alpha = .3) + -->
<!--   facet_grid(month_name~.) + -->
<!--   xlab("Date") + ylab("Monthly Food Loss and Waste (kg)") + -->
<!--   ggtitle("Monthly Food Loss and Waste Trend") -->
<!-- monthly_loss_waste -->

<!-- # Monthly Plot on food loss ------------------------------------------------ -->
<!-- monthly_loss <-  -->
<!--   ggplot(data = df, aes(x = day_name, y = food_loss_kg, group=1)) + -->
<!--   geom_line(color="black") + -->
<!--   geom_point(aes(shape = is_closed)) + -->
<!--   facet_grid(month_name~.) + -->
<!--   scale_shape_manual(values=c(16, 4))+ -->
<!--   theme(legend.position = "none") + -->
<!--   xlab("Date") + ylab("Monthly Food Loss (kg)") + -->
<!--   ggtitle("Monthly Food Loss Trend") -->
<!-- monthly_loss -->

<!-- # Monthly Plot on food waste ----------------------------------------------- -->
<!-- monthly_waste <-  -->
<!--   ggplot(data = df, aes(x = day_name, y = food_waste_kg, group=1)) + -->
<!--   geom_line(color="black") + -->
<!--   geom_point(aes(shape = is_closed)) + -->
<!--   facet_grid(month_name~.) + -->
<!--   scale_shape_manual(values=c(16, 4))+ -->
<!--   theme(legend.position = "none") + -->
<!--   xlab("Date") + ylab("Monthly Food Waste (kg)") + -->
<!--   ggtitle("Monthly Food Waste Trend") -->
<!-- monthly_waste -->

<!-- # Monthly Plot on solid food waste ----------------------------------------- -->
<!-- monthly_solid_waste <-  -->
<!--   ggplot(data = df, aes(x = day_name, y = solid_waste_kg, group=1)) + -->
<!--   geom_line(color="dark orange") + -->
<!--   geom_point(aes(shape = is_closed)) + -->
<!--   facet_grid(month_name~.) + -->
<!--   scale_shape_manual(values=c(16, 4))+ -->
<!--   theme(legend.position = "none") + -->
<!--   xlab("Date") + ylab("Monthly Solid Food Waste (kg)") + -->
<!--   ggtitle("Monthly Solid Food Waste Trend") -->
<!-- monthly_solid_waste -->

<!-- # Monthly Plot on liquid food waste ---------------------------------------- -->
<!-- monthly_liquid_waste <-  -->
<!--   ggplot(data = df, aes(x = day_name, y = liquid_waste_kg, group=1)) + -->
<!--   geom_line(color="blue") + -->
<!--   geom_point(aes(shape = is_closed)) + -->
<!--   facet_grid(month_name~.) + -->
<!--   scale_shape_manual(values=c(16, 4))+ -->
<!--   theme(legend.position = "none") + -->
<!--   xlab("Date") + ylab("Monthly Liquid ood Waste (kg)") + -->
<!--   ggtitle("Monthly Liquid Food Waste Trend") -->
<!-- monthly_liquid_waste -->

<!-- # grid.arrange(monthly_loss_waste,monthly_loss, monthly_waste, -->
<!-- #              monthly_solid_waste,monthly_liquid_waste) -->
<!-- ``` -->

## Histogram indep vars.
```{r histograms_dependents}
# Histogram of Temperature -------------------------------------------
hist_temp <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = temp_c)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Temperature - Histogram")
hist_temp
ggqqplot(df$temp_c)

# Histogram of Humidity --------------------------------------------
hist_humi <- 
  ggplot(data = subset(df, is_closed %in% FALSE),
         aes(x = humi_p)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 4, fill = 4, alpha = 0.15) +
  labs(title = "Humidity - Histogram")
hist_humi
ggqqplot(df$humi_p)

# Histogram of precipitation ----------------------------------------
hist_prep <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = log(prcp_mm+1))) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 1, fill = 4, alpha = 0.15) +
  labs(title = "Precipitation - Histogram")
hist_prep
ggqqplot((df$prcp_mm))

# Histogram of sales ----------------------------------------
hist_sales <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = sales)) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 1, fill = 4, alpha = 0.15) +
  labs(title = "Sales - Histogram")
hist_sales
ggqqplot(df$sales)

# Histogram of halfs ----------------------------------------
hist_halfs <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x = log(halfs+1))) +
  geom_histogram(aes(y = after_stat(density)), 
                 bins = 30,colour = 1, fill = "white") +
  geom_density(linewidth = 1.5, colour = 1, fill = 4, alpha = 0.15) +
  labs(title = "Halfs - Histogram")
hist_halfs
ggqqplot(log(df$halfs+1))

```

## Boxplots - weekly
```{r boxplots weekly}
# # weekly boxplot on food loss + food waste ----------------------------
# boxplot_week_loss_waste <- 
#   ggplot(data = subset(df, is_closed %in% FALSE), 
#          aes(x=day, y=food_loss_kg + food_waste_kg)) + 
#   geom_boxplot(outlier.shape=8, outlier.size=3) +
#   stat_summary(fun=mean, geom="point", shape=16, size=3) +
#   labs(title = "Boxplot of Food Loss and Food Waste in Day of the Week",
#        x = "Week of Day", y = "Food Loss and Food Waste in kg")
# boxplot_week_loss_waste
# 
# # weekly boxplot on food loss ----------------------------------
# boxplot_week_food_loss <- 
#   ggplot(data = subset(df, is_closed %in% FALSE),
#          aes(x=day, y=food_loss_kg)) + 
#   geom_boxplot(outlier.shape=8, outlier.size=3) +
#   stat_summary(fun=mean, geom="point", shape=16, size=3) +
#   labs(title = "Boxplot of Food Loss in Day of the Week",
#        x = "Week of Day", y = "Food Loss in kg")
# boxplot_week_food_loss

# weekly boxplot on food waste ------------------------------------
boxplot_week_food_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=food_waste_kg)) + 
  geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="point", shape=16, size=3) +
  labs(title = "Boxplot of All Food Waste in Day of the Week",
       x = "Week of Day", y = "Food Waste in kg")
boxplot_week_food_waste

# weekly boxplot on solid food waste ------------------------------------
boxplot_week_solidWaste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=solid_waste_kg)) + 
  geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="point", shape=16, size=3) +
  labs(title = "Boxplot of Solid Food Waste in Day of the Week",
       x = "Week of Day", y = "Solid Food Waste in kg")
boxplot_week_solidWaste

# weekly boxplot on liquid food waste ------------------------------------
boxplot_week_liquidWaste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=liquid_waste_kg)) + 
  geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="point", shape=16, size=3) +
  labs(title = "Boxplot of Liquid Food Waste in Day of the Week",
       x = "Week of Day", y = "Liquid Food Waste in kg")
boxplot_week_liquidWaste

# grid.arrange(boxplot_week_food_loss,boxplot_week_food_waste,
#              boxplot_week_solidWaste,boxplot_week_liquidWaste)
```

## Boxplots per customer - weekly
```{r boxplots customer weekly}
# weekly boxplot on food waste ------------------------------------
boxplot_week_food_waste_p <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=food_waste_kg/customers)) + 
  geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="point", shape=16, size=3) +
  labs(title = "Boxplot of Food Waste per Customer in Day of the Week",
       x = "Week of Day", y = "Food Waste per Customer in kg")
boxplot_week_food_waste_p

# weekly boxplot on solid food waste ------------------------------------
boxplot_week_solidWaste_p <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=solid_waste_kg/customers)) + 
  geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="point", shape=16, size=3) +
  labs(title = "Boxplot of Solid Food Waste per Customer in Day of the Week",
       x = "Week of Day", y = "Solid Food Waste per Customer in kg")
boxplot_week_solidWaste_p

# weekly boxplot on liquid food waste ------------------------------------
boxplot_week_liquidWaste_p <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=liquid_waste_kg/customers)) + 
  geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="point", shape=16, size=3) +
  labs(title = "Boxplot of Liquid Food Waste per Customer in Day of the Week",
       x = "Week of Day", y = "Liquid Food Waste per Customer in kg")
boxplot_week_liquidWaste_p

# grid.arrange(boxplot_week_food_loss,boxplot_week_food_waste,
#              boxplot_week_solidWaste,boxplot_week_liquidWaste)
```

## bar plot - weekly
```{r bar plots weekly}
# weekly boxplot on food waste ------------------------------------
lineplot_week_food_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=food_waste_kg)) + 
  # geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="bar", shape=16, size=3) +
  labs(title = "Boxplot of All Food Waste in Day of the Week",
       x = "Week of Day", y = "Food Waste in kg")
lineplot_week_food_waste

# weekly boxplot on solid food waste ------------------------------------
lineplot_week_solidWaste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=solid_waste_kg)) + 
  # geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="bar", shape=16, size=3) +
  labs(title = "Boxplot of Solid Food Waste in Day of the Week",
       x = "Week of Day", y = "Solid Food Waste in kg")
lineplot_week_solidWaste

# weekly boxplot on liquid food waste ------------------------------------
lineplot_week_liquidWaste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=day, y=liquid_waste_kg)) + 
  # geom_boxplot(outlier.shape=8, outlier.size=3) +
  stat_summary(fun=mean, geom="bar", shape=16, size=3) +
  labs(title = "Boxplot of Liquid Food Waste in Day of the Week",
       x = "Week of Day", y = "Liquid Food Waste in kg")
lineplot_week_liquidWaste

# grid.arrange(lineplot_week_food_loss,lineplot_week_food_waste,
#              lineplot_week_solidWaste,lineplot_week_liquidWaste)
```

## Boxplot - monthly
```{r boxplot_monthly}
# monthly boxplot on food waste ------------------------------------
boxplot_month_waste <- 
  ggplot(data = subset(df, is_closed %in% FALSE),
         aes(x=month_name, y=food_waste_kg)) + 
  geom_boxplot(outlier.shape=8, outlier.size=2) +
  stat_summary(fun=mean, geom="point", shape=16, size=2) +
  labs(title = "Boxplot of Daily Food Waste in Month",
       x = "Month", y = "Food Waste in kg")
boxplot_month_waste

# monthly boxplot on solid food waste ------------------------------------
boxplot_month_solidWaste <- 
  ggplot(data = subset(df, is_closed %in% FALSE),
         aes(x=month_name, y=solid_waste_kg)) + 
  geom_boxplot(outlier.shape=8, outlier.size=2) +
  stat_summary(fun=mean, geom="point", shape=16, size=2) +
  labs(title = "Boxplot of Daily Solid Food Waste in Month",
       x = "Monthy", y = "Solid Food Waste in kg")
boxplot_month_solidWaste

# boxplot of week of day for solid food waste ------------------------------------
boxplot_month_liquidWaste <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=month_name, y=liquid_waste_kg)) + 
  geom_boxplot(outlier.shape=8, outlier.size=2) +
  stat_summary(fun=mean, geom="point", shape=16, size=2) +
  labs(title = "Boxplot of Liquid Food Waste in Month",
       x = "Month", y = "Liquid Food Waste in kg")
boxplot_month_liquidWaste

# grid.arrange(boxplot_month_loss_waste, boxplot_month_loss,boxplot_month_waste,
#              boxplot_month_solidWaste,boxplot_month_liquidWaste)
```
## Boxplot per customer - monthly
```{r boxplot_monthly customer}
# monthly boxplot on food waste ------------------------------------
boxplot_month_waste_p <- 
  ggplot(data = subset(df, is_closed %in% FALSE),
         aes(x=month_name, y=food_waste_kg/customers)) + 
  geom_boxplot(outlier.shape=8, outlier.size=2) +
  stat_summary(fun=mean, geom="point", shape=16, size=2) +
  labs(title = "Boxplot of Food Waste per Customer in Month",
       x = "Month", y = "Food Waste per Customer in kg")
boxplot_month_waste_p

# monthly boxplot on solid food waste ------------------------------------
boxplot_month_solidWaste_p <- 
  ggplot(data = subset(df, is_closed %in% FALSE),
         aes(x=month_name, y=solid_waste_kg/customers)) + 
  geom_boxplot(outlier.shape=8, outlier.size=2) +
  stat_summary(fun=mean, geom="point", shape=16, size=2) +
  labs(title = "Boxplot of Solid Food Waste per Customer in Month",
       x = "Monthy", y = "Solid Food Waste per Customer in kg")
boxplot_month_solidWaste_p

# boxplot of week of day for solid food waste ------------------------------------
boxplot_month_liquidWaste_p <- 
  ggplot(data = subset(df, is_closed %in% FALSE), 
         aes(x=month_name, y=liquid_waste_kg/customers)) + 
  geom_boxplot(outlier.shape=8, outlier.size=2) +
  stat_summary(fun=mean, geom="point", shape=16, size=2) +
  labs(title = "Boxplot of Liquid Food Waste per Customer in Month",
       x = "Month", y = "Liquid Food Waste per Customer in kg")
boxplot_month_liquidWaste_p

# grid.arrange(boxplot_month_loss_waste, boxplot_month_loss,boxplot_month_waste,
#              boxplot_month_solidWaste,boxplot_month_liquidWaste)
```

\newpage
# Time Series Plots for Independents
```{r tsPlot_weather}
## Time Series plots of:
# 1. weather conditions: temperature, humidity, precipitation
# 2. # orders + dine in + size + liquor + daily sales (confident)

# Time Series Plot on temperature ---------------------------------
tsPlot_temp <- 
  ggplot(data = df, aes(x = as.Date(date), y = temp_c)) +
  geom_point() +
  stat_smooth(method = "loess", color = "green", fill = "green",
              formula = y~x) +
  # geom_line(aes(group = 1), color="orange") +
  geom_hline(aes(yintercept = 22), linetype='dotted') +
  scale_x_date(date_labels = "%b %d") +
  xlab("Date") + ylab("Temperature in Degree Celsius") +
  ggtitle("Daily Average Hourly Temperature Plot")
tsPlot_temp

# Time Series Plot on gap temperature with 22C---------------------------------
tsPlot_temp_gap <- 
  ggplot(data = df, aes(x = as.Date(date), y = temp_c-22)) +
  geom_point() +
  stat_smooth(method = "loess", color = "green", fill = "green",
              formula = y~x) +
  # geom_line(color="green") +
  scale_x_date(date_labels = "%b %d") +
  xlab("Date") + ylab("Gap Temperature in Degree Celsius") +
  ggtitle("Daily Gap Temperature Plot")
tsPlot_temp_gap

# Time Series Plot on humidity ---------------------------------
tsPlot_humidity <- 
  ggplot(data = df, aes(x = as.Date(date), y = humi_p)) +
  geom_point() +
  stat_smooth(method = "loess", color = "green", fill = "green",
              formula = y~x) +
  # geom_line(color="red") +
  scale_x_date(date_labels = "%b %d") +
  xlab("Date") + ylab("Humidity in Percent") +
  ggtitle("Daily Humidity Plot")
tsPlot_humidity

# Time Series Plot on precipitation ---------------------------------
tsPlot_precip <- 
  ggplot(data = df, aes(x = as.Date(date), y = prcp_mm)) +
  geom_point() +
  stat_smooth(method = "loess", color = "green", fill = "green",
              formula = y~x) +
  # geom_line(color="blue") +
  scale_x_date(date_labels = "%b %d") +
  xlab("Date") + ylab("Precipitation in millimetre") +
  ggtitle("Daily Precipitation Plot")
tsPlot_precip

# grid.arrange(tsPlot_temp,tsPlot_temp_gap,tsPlot_humidity, tsPlot_precip)
```


```{r tsPlot_business}
## Time Series plots of:
# 1. # orders (full, half, takeouts)
# 2. daily dine in served (kg)
# 4. liquor
# 5. daily sales (confident)

# Time Series Plot on Meal Orders ---------------------------------
tsPlot_total_orders <- 
  ggplot(data = subset(df, is_closed %in% FALSE), aes(x=as.Date(date))) +
  geom_line(aes(y = fulls, color="fulls")) +
  geom_line(aes(y = halfs, color="halfs")) +
  scale_x_date(date_labels = "%b %d") +
  geom_line(aes(y = takeouts, color="takeouts"), linetype = "dashed") +
  xlab("Date") + ylab("Daily Number of Meal Orders") +
  ggtitle("Daily Different Package Meal Orders Plot")+
  scale_color_manual(name='Packages',
                     breaks=c('fulls', 'halfs', 'takeouts'),
                     values=c('fulls' = 'dark blue',
                              'halfs' = 'purple', 
                              'takeouts'='dark red')) +
  theme(legend.position = "right")
tsPlot_total_orders

# Time Series Plot on demand and production ---------------------------------
tsPlot_D_S <- 
  ggplot(data = subset(df, is_closed %in% FALSE), aes(x = as.Date(date))) +
  geom_line(aes(y = daily_total_served), color="dark blue") +
  geom_line(aes(y = FL_FP_kg), color="dark red", linetype = "dashed") +
  scale_x_date(date_labels = "%b %d") +
  xlab("Date") + ylab("Daily Quantity in kg") +
  ggtitle("Daily Total Served and Production Plot") +
  scale_color_manual(name='Served',
                     breaks=c('daily_total_served', 'FL_FP_kg'),
                     values=c('daily_total_served' = 'dark blue',
                              'FL_FP_kg' = 'dark red')) +
  theme(legend.position = "right")
tsPlot_D_S

tsPlot_diff_D_S <- 
  ggplot(data = subset(df, is_closed %in% FALSE), aes(x = as.Date(date))) +
  geom_line(aes(y = daily_total_served - FL_FP_kg), color="black") +
  stat_smooth(aes(y = daily_total_served - FL_FP_kg), method = "loess",
              color = "light green", fill = "light green") +
  scale_x_date(date_labels = "%b %d") +
  xlab("Date") + ylab("Daily Inventory in kg") +
  ggtitle("Difference Between Total Served and Production Plot")
tsPlot_diff_D_S

# Time Series Plot on precipitation ---------------------------------
tsPlot_sales <- 
  ggplot(data = subset(df, is_closed %in% FALSE),aes(x = as.Date(date))) +
  geom_line(aes(y = sales), color="purple") +
  scale_x_date(date_labels = "%b %d") +
  stat_smooth(aes(y = sales), method = "loess",
              color = "light green", fill = "light green") +
  xlab("Date") + ylab("Daily Sales in dollar") +
  ggtitle("Daily Sales Plot")
tsPlot_sales

# grid.arrange(tsPlot_total_orders,tsPlot_D_S, tsPlot_diff_D_S,tsPlot_sales)
```

## (Partial and) Autocorrelation Function
```{r acf pacf}
## acf and pacf ----------------------------------------------------------------
# acf and pacf for food loss ---------------------------------------------------
acf_fl  <- ggAcf(as.ts(df$food_loss_kg))
pacf_fl <- ggPacf(as.ts(df$food_loss_kg))
# acf and pacf for all food waste ----------------------------------------------
acf_fw  <- ggAcf(as.ts(df$food_waste_kg))
pacf_fw <- ggPacf(as.ts(df$food_waste_kg))
# acf and pacf for solid food waste --------------------------------------------
acf_sfw  <- ggAcf(as.ts(df$solid_waste_kg))
pacf_sfw <- ggPacf(as.ts(df$solid_waste_kg))
# acf and pacf for liquid food waste -------------------------------------------
acf_lfw  <- ggAcf(as.ts(df$liquid_waste_kg))
pacf_lfw <- ggPacf(as.ts(df$liquid_waste_kg))


grid.arrange(acf_fl,pacf_fl)
grid.arrange(acf_fw,pacf_fw)
grid.arrange(acf_sfw,pacf_sfw)
grid.arrange(acf_lfw,pacf_lfw)
```

\newpage
## Spectral Analysis
```{r spec_all}
# spectrum analysis for food loss ---------------------------------------------
# plot.spectrum(dt$allWasteKg)
raw.spec_fl <- list(spec.pgram(df$food_loss_kg, spans = 10))
1/raw.spec_fl[[1]]$freq[which.max(raw.spec_fl[[1]]$spec)]

# spectrum analysis for food waste ---------------------------------------------
# plot.spectrum(dt$allWasteKg)
raw.spec_fw<- list(spec.pgram(df$food_waste_kg, spans = 10))
1/raw.spec_fw[[1]]$freq[which.max(raw.spec_fw[[1]]$spec)]

# spectrum analysis for food waste ---------------------------------------------
# plot.spectrum(dt$allWasteKg)
raw.spec_sfw<- list(spec.pgram(df$solid_waste_kg, spans = 10))
1/raw.spec_sfw[[1]]$freq[which.max(raw.spec_sfw[[1]]$spec)]

# spectrum analysis for food waste ---------------------------------------------
# plot.spectrum(dt$allWasteKg)
raw.spec_lfw<- list(spec.pgram(df$liquid_waste_kg, spans = 10))
1/raw.spec_lfw[[1]]$freq[which.max(raw.spec_lfw[[1]]$spec)]
```
roughly 6 (days) period for food waste,
but food loss is approx. 3 days or 20 days cycle.


```{r delete envir}
### Erase states
rm(list = ls()[! ls() %in% c("df", "AdjMat")])
```

